---
title: "3PG example"
author: "Jinyan Yang"
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_float: true
    code_folding: true
---
```{r message=F, include=FALSE}
library('r3PG')
```

We will now use real data from Cumberland Plain Woodland (-33.6166, 150.7377). We need to first read in meteorology data and then obtain plant physiological parameters.

Here we will go through changing each input files (met,species,thinning and parameters).

### 1 Met data

Our site is in Richmond NSW, dominated by E.tereticornis Sm. The site has a mean annual temperature of 17 $^\circ C$ and a mean annual precipitation of 800mm.

Let’s now read and look at the met data.

```{r}
met.df <- read.csv('e:/repo/3pg/rmd/ros.met.csv')

plot(met.df$prcp,xlab='',ylab = 'prcp')

plot(met.df$srad,xlab='',ylab = 'srad')
```

We need to put in number of frost days and  $CO_{2}$ data. 

```{r}
# 
met.df$frost_days <- 0
# 
met.df$co2 <- 400
met.df$srad <- 2.3 * met.df$srad
```

### 2 Site information

```{r}
site.new <- d_site

site.new$latitude <- -38
site.new$altitude <- 50
site.new$soil_class <- 2
site.new$asw_i <- 150
site.new$asw_min <- 50
site.new$asw_max <- 300
site.new$from <- '2019-01'
site.new$to <- '2020-12'
```


### 3 Species composition

Since we are using only one species, the inputs are just the initial conditions of the species.

```{r}
spc.new <- d_species[1,]
spc.new$species <- 'ET'
spc.new$planted <- '1900-01'
spc.new$fertility <- 1
spc.new$stems_n <- 400
spc.new$biom_stem <- 90
spc.new$biom_root <- 10
spc.new$biom_foliage <- 0.2
```


### 4 Plant physiology

Let see if our spcecies has been reported by previous literature.

```{r}
list.spc <- get_parameters(mode = "overview", sp_names = NULL)

e.list <- list.spc$species[grep(pattern = 'Eucalyptus',x = list.spc$species)]

print(e.list)
```

We did not find our species but a similar one, E.globulus. We are going to use the most of the parameters from E.globulus as example.

```{r}
et.df <- get_parameters(mode = "full", sp_names = 'Eucalyptus globulus')

et.sub <- subset(et.df[4,],select = -c(source_full,species,
                                       link,notes,parset_id,     
                                       source,source_comments,
                                       country,age,type,year,region))
# 
par.new <- d_parameters[,c(1,3)]
names(par.new)[2] <- 'ET'
# 
par.new$ET[par.new$parameter == 'SLA0'] <- 50
par.new$ET[par.new$parameter == 'SLA1'] <- 50

par.new$ET[par.new$parameter == 'MaxAge'] <- 500
par.new$ET[par.new$parameter == 'LAImaxIntcptn'] <- 3

par.new$ET[par.new$parameter == 'alphaCx'] <- et.sub$alphaCx
par.new$ET[par.new$parameter == 'fCalpha700'] <- 1.8
par.new$ET[par.new$parameter == 'fCg700'] <- 0.6

par.new$ET[par.new$parameter == 'Tmin'] <- et.sub$Tmin
par.new$ET[par.new$parameter == 'Topt'] <- et.sub$Topt
par.new$ET[par.new$parameter == 'Tmax'] <- et.sub$Tmax

par.new <- par.new[,c('parameter','ET')]
```


### 4 Self-thinning

We are looking at a mature forest so self-thinning is not a concern– it has been done already. For demonstration purpose, we use the thinning data from Fagus sylvatica.

```{r}
# 
thin.new <- d_thinning[1,]

thin.new$species <- 'ET'

thin.new$age <- 200
# 
size.new <- (d_sizeDist[,1:2])
names(size.new)[2] <- 'ET'
```

Now we can run the model!

### 5 Normal run

```{r}
met.df$co2 <- 400
out.et <- run_3PG(site = site.new,
                  species = spc.new,
                  climate = met.df,
                  thinning = thin.new,
                  parameters = par.new,
                  size_dist = size.new,
                  settings = list(light_model = 2, 
                                  transp_model = 2, phys_model = 2,
                                  correct_bias = 0, calculate_d13c = 0),
                  check_input = TRUE, 
                  df_out = TRUE)

# 
met.df$co2 <- 550
out.et.eco2 <- run_3PG(site = site.new,
                  species = spc.new,
                  climate = met.df,
                  thinning = thin.new,
                  parameters = par.new,
                  size_dist = size.new,
                  settings = list(light_model = 2, 
                                  transp_model = 2, phys_model = 2,
                                  correct_bias = 0, calculate_d13c = 0),
                  check_input = TRUE, 
                  df_out = TRUE)
```

Let's check the change in GPP. 

```{r}
par(mar=c(5,5,1,1))
palette(c(rainbow(3)))
plot(value~date,data = out.et.eco2[out.et.eco2$species == 'ET' &
                                 out.et.eco2$variable == 'gpp',],
       type='l',xlab='',ylab=expression('GPP'~(t~DM~ha^-1)),col=1)
  
  points(value~date,data = out.et[out.et$species == 'ET' &
                                   out.et$variable == 'gpp',],
         type='l',xlab='',col=2)
  
  legend('topleft',legend = c('high','current'),
         lty='solid',col=palette(),bty='n',horiz = T)


```

Or explore the impact of $CO_{2}$

```{r}
par(mar=c(5,5,1,1))
palette(c(rainbow(3)))
plot(value~date,data = out.et.eco2[out.et.eco2$species == 'ET' &
                                 out.et.eco2$variable == 'transp_veg',],
       type='l',xlab='',
     ylab=expression('Tranpiration'~(mm~month^-1)),col=1)
  
  points(value~date,data = out.et[out.et$species == 'ET' &
                                   out.et$variable == 'transp_veg',],
         type='l',xlab='',col=2)
  
  legend('topleft',legend = c('high','current'),
         lty='solid',col=palette(),bty='n',horiz = T)


```